IGRINS spectra of \name

### 2016-06-01 document/ms.tex
Some new and updated notebooks include results from all of H-band
GJH adds new content to the manuscript including low res spectra and photometry, some prose.

\author{Michael A. Gully-Santiago,\altaffilmark{1} Greg Herczeg,\altaffilmark{1} et al.}

@@

In this paper we characterize the starspot coverage and temperature contrast of \name using full spectrum fitting.  We chose \name for its likelihood of large areal coverage of starspots, as evinced by large-amplitude photometric variability  detected in $BVRI$ bands.  Its period is 3.37$\pm$0.01 days \citep{1993AJ....106.1608V,1994IBVS.4042....1G}.  Recent optical spectro-polarimetry showed evidence for hot or cool starspots covering an estimated $25\%$ of the stellar surface \citep{2014MNRAS.444.3220D}.  The source has little or no accretion ($\log{\dot M} < 8.1$), no detection of mid-infrared nor mm excess, and no stellar companion, so its spectrum should be devoid of complicating factors like near-IR excess veiling and accretion excess.  This source is the ideal candidate for direct measurement of two-temperature photosphere due to starspots.

@@

\begin{figure*}
	\centering
	\includegraphics[width=0.95\textwidth]{figures/V_phot_phase.pdf}
	\caption{Estimated $V$-band photometry phase during the times of observations.}
	\label{fig:PhotPhase}
\end{figure*}

@@

>>>>

\author{Michael A. Gully-Santiago,\altaffilmark{1} Gregory J. Herczeg,\altaffilmark{1} et al.}

@@

In this paper we characterize the starspot coverage and temperature contrast of \name using full spectrum fitting.  We chose \name for its likelihood of large areal coverage of starspots, as evinced by large-amplitude photometric variability  detected in $BVRI$ bands.  Its period is 3.37$\pm$0.01 days \citep{1993AJ....106.1608V,1994IBVS.4042....1G,grankin08,xiao12}.  Recent optical spectro-polarimetry showed evidence for hot or cool starspots covering an estimated $25\%$ of the stellar surface \citep{2014MNRAS.444.3220D}.  The source has little or no accretion ($\log{\dot M} < 8.1$), no detection of mid-infrared nor mm excess, and no stellar companion, so its spectrum should be devoid of complicating factors like near-IR excess veiling and accretion excess.  This source is the ideal candidate for direct measurement of two-temperature photosphere due to starspots.

@@

\begin{figure*}
	\centering
	\includegraphics[width=0.95\textwidth]{figures/phase_folded_lightcurve.pdf}
	\caption{Phase of photometry at the time of IGRINS measurement}
	\label{fig:PhotPhase}
\end{figure*}

@@

\section{Monitoring the Spots of LkCa 4}

The previous sections established that the high resolution optical and near-IR spectra of LkCa 4 may be explained by a cool photosphere with a hot spot.  In this section, we will demonstrate that this same model explains the broadband spectral energy distribution and flux-calibrated optical/near-IR spectra of LkCa 4.  Periodic variability in photometry and spectral indices are reproduced by modest changes in the visible fraction of the hot spot.

\subsection{Reproducing the Spectral Energy Distribution}

\subsection{Reproducing the flux-calibrated low resolution}

Figure~\ref{fig:lores}...

\subsection{TiO Variability}

The depth of TiO and other molecular bands are a common diagnostic of spectral type (and temperature) in optical spectra.  In the 12 ESPaDOnS spectra of \name\ obtained over 14 days \citep{2014MNRAS.444.3220D}, the depth of the TiO bands vary.

Each of the TiO spectral index is correlated with the other indices.  The line depths also correlate with the V-band magnitude, as estimated from the ASAS-SN photometry and the V-band photometry provided in \citep{2014MNRAS.444.3220D} that were obtained within 6 months of the ESPaDOnS observations.

Needs a lot more.

\subsection{Phased colors}

\begin{figure*}
	\centering
	\includegraphics[width=0.95\textwidth]{lkca4_lores} 
	\vspace{-100mm}
	\caption{The low-resolution optical/near-IR spectrum of LkCa 4 is }
	\label{fig:lores}
\end{figure*}

\begin{figure*}
	\centering
	\includegraphics[width=0.95\textwidth]{tiovar} 
	\vspace{-100mm}
	\caption{Variability in TiO bands measured with ESPaDOnS (see also Table X).  The V-band emission is estimated from fits to the ASAS-SN lightcurve obtained during the same period.  The main panel shows a correlation between V-band magnitude and the TiO-7140 index, while the inset shows a similar correlation with the average of the TiO 6200, CaH 6800, and TiO 7600 indices.}
	\label{fig:tiovar}
\end{figure*}
